### 2017-10-07 TF-vldb2018/full/sec-appendix.tex

\begin{figure*}[tb!]
	%\begin{widepage}
	\vspace{-1.5ex}
	\begin{center}
		\hspace{-8ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{2ex}
			\begin{center}
				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
		\hspace{20ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{-0.6ex}
			\begin{center}
				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
					\includegraphics[scale=0.29]{./fig/inc-complexity-proof-pattern.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
	\end{center}
	\vspace{-3ex}
	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
	%\label{exp-semantic-effectiveness-citation}
	%\end{widepage}
	\vspace{-2.0ex}
\end{figure*}

@@

\vspace{-1.5ex}
\etitle{(I) \dynteamF\, is unbounded for unit data update}.
%Following \cite{Reps96, FanWW13-tods},
Consider the following pattern and data graph, and unit data updates.
Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
Let pattern graph be a triangle with nodes $a$, $b$ and $c$ with labels $A$, $B$ and $C$ respectively.
Consider two unit edge insertions $\delta_1$ = $(c_n$, $a_{n+1})^+$ and $\delta_2$ = $(c_{2n}$, $a_1)^+$,
and set $k = 1$ and $r$ = $6n$.
Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(P, H_1) = L_{k}(P, H_2) = \emptyset$,
while $L_{k}(P, H_1\oplus \delta_2) \neq \emptyset$.
Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(G', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some graph $G'$.
Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$.
However, $H_1$ was obtained from $G$ by applying update $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$.
Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$.
As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying change $\delta'$ to graph $G'$,
then every node on some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on the path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively.
Hence, the time taken for processing update $\delta_1$ to $G$ plus the time taken for processing update $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of the incremental algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.

@@

\vspace{-1.5ex}
\etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
Consider the following pattern and data graph, and unit pattern updates.
Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
where $a'_i$, $b'_i$, $c'_i$ and $d'_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$),
where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Consider two unit edge deletions $\delta_1$ = $(a_1$, $c_1)^-$ and $\delta_2$ = $(b_{n+1}$, $d_{n+1})^-$,
and set $k = 1$ and $r$ = $4m$.
Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(H_1, G) = L_{k}(H_2, G) = \emptyset$,
while $L_{k}(H_1\oplus \delta_2, G) \neq \emptyset$.
Assume there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(P', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some pattern $P'$.
Now consider two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes in $G$ for $H_1\oplus \delta_2$ are affected, while no node in $G$ for $P\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage,
this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in $P$ and $H_1$.
However, $H_1$ was obtained from $P$ by applying $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$.
Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$.
%As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying update $\delta'$ to pattern $P'$,
%then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
According to the characteristics of locally persistent algorithms as illustrated in the data updates case,
$Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on the path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively.
Hence, the time taken for processing $\delta_1$ to $P$ plus the time taken for processing $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $4n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.
That is, \dynteamF\, is unbounded even for $k=1$ and unit pattern update.

@@

\vspace{4ex}
\noindent
{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\vspace{-0.5ex}

We also used another real-life dataset {\em \youtube}~\cite{youtubeWeb} for experimental verification.
It contains 2.03M video nodes and 12.2M edges, which represent recommendations between two videos. We used the undirected version, and generated 400 labels based on the built-in categories and ages of videos.

\vspace{-1.5ex}
The experimental results on \youtube are reported here.

\vspace{-1.8ex}
\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis, \denalk on \youtube \wrt four quality measures.
The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
We find \optgrouprec strikes a balance at capturing the practical requirements.

>>>>

\begin{figure*}[tb!]
	%\begin{widepage}
	\vspace{-1.5ex}
	\begin{center}
		\hspace{-8ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{2ex}
			\begin{center}
				\subfigure[{Unit data update}]{\label{fig-inc-complexity-data}
					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
			\end{center}
			\vspace{-2.5ex}
		\end{minipage}
		\hspace{20ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{-0.6ex}
			\begin{center}
				\subfigure[{Unit pattern update}]{\label{fig-inc-complexity-pattern}
					\includegraphics[scale=0.29]{./fig/inc-complexity-proof-pattern.eps}}
			\end{center}
			\vspace{-2.5ex}
		\end{minipage}
	\end{center}
	\vspace{-4ex}
	\caption{Unboundedness of unit data and pattern update}
	\label{proof-patdata-inc}
	%\end{widepage}
	\vspace{-3.0ex}
\end{figure*}

@@

\vspace{-1.5ex}
\etitle{(I) \dynteamF\, is unbounded for unit data update}.
%Following \cite{Reps96, FanWW13-tods},
Consider the following pattern and data graph, and unit data updates, as shown in Fig.~\ref{proof-patdata-inc} (a).
Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
Let pattern graph be a triangle with nodes $a$, $b$ and $c$ with labels $A$, $B$ and $C$ respectively.
Consider two unit edge insertions $\delta_1$ = $(c_n$, $a_{n+1})^+$ and $\delta_2$ = $(c_{2n}$, $a_1)^+$,
and set $k = 1$ and $r$ = $6n$.
Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(P, H_1) = L_{k}(P, H_2) = \emptyset$,
while $L_{k}(P, H_1\oplus \delta_2) \neq \emptyset$.
Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(G', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some graph $G'$.
Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$.
However, $H_1$ was obtained from $G$ by applying update $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$.
Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$.
As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying change $\delta'$ to graph $G'$,
then every node on some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on the path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively.
Hence, the time taken for processing update $\delta_1$ to $G$ plus the time taken for processing update $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of the incremental algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.

@@

\vspace{-1.5ex}
\etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
Consider the following pattern and data graph, and unit pattern updates, as shown in Fig.~\ref{proof-patdata-inc} (b).
Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
where $a'_i$, $b'_i$, $c'_i$ and $d'_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$),
where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Consider two unit edge deletions $\delta_1$ = $(a_1$, $c_1)^-$ and $\delta_2$ = $(b_{n+1}$, $d_{n+1})^-$,
and set $k = 1$ and $r$ = $4m$.
Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(H_1, G) = L_{k}(H_2, G) = \emptyset$,
while $L_{k}(H_1\oplus \delta_2, G) \neq \emptyset$.
Assume there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(P', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some pattern $P'$.
Now consider two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes in $G$ for $H_1\oplus \delta_2$ are affected, while no node in $G$ for $P\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage,
this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in $P$ and $H_1$.
However, $H_1$ was obtained from $P$ by applying $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$.
Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$.
%As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying update $\delta'$ to pattern $P'$,
%then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
According to the characteristics of locally persistent algorithms as illustrated in the data updates case,
$Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on the path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively.
Hence, the time taken for processing $\delta_1$ to $P$ plus the time taken for processing $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $4n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.
That is, \dynteamF\, is unbounded even for $k=1$ and unit pattern update.

@@

\noindent
{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\vspace{-0.5ex}
The experimental results on \youtube are reported here.

\vspace{-1.8ex}
\stitle{Exp-1: Performance of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk on \youtube \wrt four quality measures.
The results are reported in Fig.~\ref{fig-exp-semantic-youtube-diameter} to~\ref{fig-exp-semantic-youtube-link-varyk}.
We find \optgrouprec strikes a balance at capturing the practical requirements.
